Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-13 paper.tex
Edited paper.tex via GitHub
Tidy up end of web apps

A specific example of
this initiative is the ChemDoodle Web Components library
\cite{ChemDoodleWeb}, produced by iChemLabs. The ChemDoodle Web
Components library is open source under the GPL v3 license with a
liberal HTML exception. ChemDoodle Web Components allow the scientist
to present publication quality 2D and 3D graphics and animations for
chemical structures, reactions and spectra. Beyond graphics, this tool
provides a framework for user interaction to create dynamic
applications through web browsers, desktop platforms and mobile
devices such as the iPhone, iPad and Android devices. It is now easier
than ever for scientists to create web-based scientific content,
without having to master complicated technologies such as Java
applets. iChemLabs is dedicated to funding, developing and supporting
the library to ensure that the next generation of scientific
applications is easily achievable by academia, government and
industry. This goal helps to make sure that the cost of education
decreases while using the web to further spread science.

>>>>

In 2009, iChemLabs released the ChemDoodle Web Components
library~\cite{ChemDoodleWeb} under the GPL v3 license (with a
liberal HTML exception). This library is completely implemented in JavaScript
and uses HTML5 to allow the scientist
to present publication quality 2D and 3D graphics and animations for
chemical structures, reactions and spectra. Beyond graphics, this tool
provides a framework for user interaction to create dynamic
applications through web browsers, desktop platforms and mobile
devices such as the iPhone, iPad and Android devices.
